Generate Mortality Adjustment for FEM

### 2021-01-25 FEM_R/mortality_adjustment.Rmd
Finished replacing the mortality adjustment using ONS data on mortality rate (qx)

```{r}
# Rename age column and filter out ages below 50
male <- m_cohort %>% 
            rename(age = 'Attained age (years)') %>%
            filter(age >= 50)

female <- f_cohort %>% 
            rename(age = 'Attained age (years)') %>%
            filter(age >= 50)

# Add a column for gender and reinsert the rownames back as a column for reshaping
m_copy <- cbind(male = 1, rownames(m_copy), m_copy)
rownames(m_copy) <- 1:nrow(m_copy)
f_copy <- cbind(male = 0, rownames(f_copy), f_copy)
rownames(f_copy) <- 1:nrow(f_copy)
# Rename age column
m_copy <- rename(m_copy, age = "rownames(m_copy)")
f_copy <- rename(f_copy, age = "rownames(f_copy)")

@@

```{r}
# Rename age column and filter out ages below 50
male <- m_cohort %>% 
            rename(age = 'age (years)') %>%
            filter(age >= 50)

female <- f_cohort %>% 
            rename(age = 'age (years)') %>%
            filter(age >= 50)

@@

# Add a column for gender and reinsert the rownames back as a column for reshaping
m_copy <- cbind(male = 1, rownames(m_copy), m_copy)
rownames(m_copy) <- 1:nrow(m_copy)
f_copy <- cbind(male = 0, rownames(f_copy), f_copy)
rownames(f_copy) <- 1:nrow(f_copy)
# Rename age column
m_copy <- rename(m_copy, age = "rownames(m_copy)")
f_copy <- rename(f_copy, age = "rownames(f_copy)")

@@

@@

>>>>

@@

```{r}
# Rename age column and filter out ages below 50
male <- m_cohort %>% 
            dplyr::rename(age = 'age (years)') %>%
            filter(age >= 50)

female <- f_cohort %>% 
            dplyr::rename(age = 'age (years)') %>%
            filter(age >= 50)

@@

# Add a column for gender and reinsert the rownames back as a column for reshaping
m_copy <- cbind(male = 1, rownames(m_copy), m_copy)
rownames(m_copy) <- 1:nrow(m_copy)
f_copy <- cbind(male = 0, rownames(f_copy), f_copy)
rownames(f_copy) <- 1:nrow(f_copy)
# Rename age column
m_copy <- dplyr::rename(m_copy, age_elsa = "rownames(m_copy)")
f_copy <- dplyr::rename(f_copy, age_elsa = "rownames(f_copy)")

@@

## Now check against US mortality adjustment

@@

# Old Defunkt

```{r}
# Rename age column and filter out ages below 50

male <- m_cohort %>% 
            dplyr::rename(age = "Attained age (years)") %>%
            filter(age >= 50)

female <- f_cohort %>% 
            dplyr::rename(age = "Attained age (years)") %>%
            filter(age >= 50)

# Add a column for gender and reinsert the rownames back as a column for reshaping
m_copy <- cbind(male = 1, rownames(m_copy), m_copy)
rownames(m_copy) <- 1:nrow(m_copy)
f_copy <- cbind(male = 0, rownames(f_copy), f_copy)
rownames(f_copy) <- 1:nrow(f_copy)
# Rename age column
m_copy <- dplyr::rename(m_copy, age = "rownames(m_copy)")
f_copy <- dplyr::rename(f_copy, age = "rownames(f_copy)")
